How to Write Theses\\ With Two Line Titles

### 2019-08-25 chapters/introduction/introduction.tex
Updates from Overleaf

Machine learning has gained rapid popularity in the past decade and different sectors like healthcare, finance, retail, etc. are using machine learning to provide better products and services. This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases. Machine learning has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.  While developing and training a machine learning model, the developers rely on the accuracy of the libraries to produce best results. The aim is to create a model that makes the best predictions.
Conventionally, oracles have been used to test the correctness of a program. Oracles provide expected values against which the output from the program can be compared and validated. Lack of reliable oracles for testing machine learning algorithms makes it very hard to test the accuracy of such programs. This problem is called the oracle problem\cite{Weyuker}. Oracle problem arises when either:
\begin{itemize}
  \item An oracle does not exist, or,
  \item An oracle can theoretically exist but it is computationally too expensive to determine the output.
\end{itemize}
Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Murphy}. Davis and Weyuker describe these set of programs as \enquote{Programs which were written in order to determine the answer in the first place. There would be no need to write such programs if the correct answer were known}\cite{Davis1981}. Most machine learning programs fall under this category as they are written in order to predict the correct answers in the first place. Several techniques can be employed to verify the correctness of such programs. One of the most popular methods being the use of pseudo-oracles. To use pseudo-oracle two or more implementations of the algorithm are independently developed to fulfill the same specification. They are run on the same input test data and the outputs from them are then compared. If the outputs match it can be asserted that the original results are according to the specification. This kind of testing is often referred to as dual coding. However, this technique introduces a significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs and is more suitable for mission-critical systems\cite{Weyuker}.\newline

>>>>

Machine learning has gained rapid popularity in the past decade and different sectors like healthcare, finance, retail, etc. are using machine learning to provide better products and services. This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases. Machine learning has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.  While developing and training a machine learning model, the developers rely on the accuracy of the libraries to produce best results. The aim is to create a model that makes the best predictions.
Conventionally, oracles have been used to test the correctness of a program. Oracles provide expected values against which the output from the program can be compared and validated. Lack of reliable oracles for testing machine learning algorithms makes it very hard to test the accuracy of such programs. This problem is called the oracle problem\cite{Weyuker}. Oracle problem arises when either:
\begin{itemize}
  \item An oracle does not exist, or,
  \item An oracle can theoretically exist but it is computationally too expensive to determine the output.
\end{itemize}
Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}. Davis and Weyuker describe these set of programs as \enquote{Programs which were written in order to determine the answer in the first place. There would be no need to write such programs if the correct answer were known}\cite{Davis1981}. Most machine learning programs fall under this category as they are written in order to predict the correct answers in the first place. Several techniques can be employed to verify the correctness of such programs. One of the most popular methods being the use of pseudo-oracles. To use pseudo-oracle two or more implementations of the algorithm are independently developed to fulfill the same specification. They are run on the same input test data and the outputs from them are then compared. If the outputs match it can be asserted that the original results are according to the specification. This kind of testing is often referred to as dual coding. However, this technique introduces a significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs and is more suitable for mission-critical systems\cite{Weyuker}.\newline

### 2019-08-25 chapters/litReview/MRMLalgo.tex
Updates from Overleaf

\section{Testing Machine Learning Programs}
Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations in order to transform inputs.
\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy2008}}
In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. Non-testable programs can be tested in one of the two ways:
\begin{itemize}
  \item Creating multiple implementations of the same program and testing them on same inputs and comparing the results. If the outputs are not same then either of the implementations can contain error. This approach is called pseudo-oracle.
  \item In absence of multiple oracle, metamorphic testing can be used. In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs. If similar outputs are not observed then there must be a defect.
\end{itemize}
STU

Murphy, Kaiser, Hu, and, Wu (2008) created a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning software. These set of properties can be used to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications\cite{Murphy2008}. Similar work has also been done by Xie et al.(2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
Murphy et al. investigated two supervised algorithms MartiRank and SVM-Light and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms.

The problem with some of the current machine learning frameworks like: Weka and Orange is that they compare the quality of results but don’t evaluate the correctness of the results. The authors apply metamorphic testing to three ML applications: MartiRank, SVM-Light, PAYL.
MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model. The algorithm then performs similar operations from the model on the test data to produce a ranking list. SVM-Light is an open-source implementation of SVM that also has a ranking mode. The authors also investigated an intrusion detection system called PAYL. PAYL is an unsupervised machine learning system. It’s dataset simply consist of TCP/IP network payloads(stream of bytes) without any label or classification.
Based on the analysis of MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model. Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before. Thus, the metamorphic properties identified were: addition and multiplication. Applying the model on two sets of data, one of which created from the other, either by multiplying a positive number or, adding a constant number, should not change the ranking. Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs thus, MartiRank also has permutative metamorphic property. Multiplying the data by a negative constant value will create a new sorting order which can easily predicted. The only change to the model will be the sorting direction i.e. the algorithm will change the sorting direction but keep the sorting order intact. Thus, MartiRank also displays an invertive metamorphic property where the output can be predicted by taking the opposite of input. MartiRank also includes inclusive and exclusive metamorphic properties. Knowing the model can help predict the position of any new elements.

\subsection{Application of Metamorphic Testing to Supervised Classifiers \cite{Xie2009}}
Building on the previous paper, the authors explore the metamorphic relations based on expected behavior of given machine learning problems. They present a case study on Weka, a popular machine learning framework, which is also the foundation for computational science tools such as BioWeka in bioinformatics. In this paper the authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms. Previously, they researched on Support Vector Machines.
In this paper the authors seek to identify the metamorphic relations for the two algorithms (kNN and NBC). NBC and kNN both calculates the mean and standard deviation of the input data. Thus, the metamorphic relations identified are:
Permuting the order of input data does not affect the mean or standard deviation.
Multiplying the data with -1 does not affect the standard deviation since, the deviation from the mean will still be the same.
Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.
From the study of these algorithms, the authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
\begin{enumerate}
  \item Consistency with affine transformation.
  \item Permutation of class labels.
  \item Permutation of attributes.
  \item Addition of uninformative/informative attributes.
  \item Consistency with re-prediction.
  \item Addition of training samples.
  \item Addition of classes by duplicating/re-labeling samples.
  \item Removal of classes/samples.
\end{enumerate}
Next, the authors introduce the notion of validation and verification. Validation refers to choosing the most appropriate algorithm to solve a problem. Verification refers to whether the implemented algorithm is correct or not. Current, software testing methods have not addressed the problem of validation and only focus on verification.
The authors then performed an experiment to verify the correctness of Weka. They created a set of random input data and used the above metamorphic relationships to generate another set of inputs. Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithm. It was observed that several MRs violated NBC algorithms. Violations in the MRs that are necessary properties imply defects in implementation. In the case of kNN algorithm, none of the necessary MRs were violated which means that there are no implementation error as per the testing.

\subsection{Dataset Coverage for Testing Machine Learning Computer Programs \cite{Nakajima2016}}
Recently, computer programs for Big Data analytics or statistical machine learning have become essential components of intelligent software systems. Test oracles are rarely available for them, and this unavailability of test oracles is known as the oracle problem. Machine learning programs are a typical instance of non-testable programs and are of the known unknowns type. Metamorphic testing (MT) is a method for tackling the oracle problem. Metamorphic relations (MR) play a role as pseudo oracles to check whether executions of the same program differ for two different test inputs. The test inputs are related by translation functions derived from metamorphic properties so that the relationship between the two results is predictable. If the results coincide with each other, the program behavior is relatively correct.
This paper studies the characteristics of the supervised learning classifiers (SUT).
Identifying Quasi-testable Core: A program component, function or procedure, is quasi-testable if we have appropriate pseudo oracles or metamorphic relations. The result of the program execution embodies uncertainty because the output is accompanied by the statistical classification performance. The classifier itself is non-testable. However, pseudo oracles with a MT can be used for testing.\par
Dataset Coverage: Test coverage is essential in software testing because it is a basis to measure how much of the SUT is checked with a set of the input test data. The graph coverage is the most popular model for software testing because it captures the structural characteristics of software artifacts, such as control-flows or data-flows of a computer program. The paper introduces the notion of dataset coverage to focus on the characteristics of the population distribution in the training dataset. However, complete coverage is not possible. The number of possible populations in datasets is also infinite.\par
SVM: A support vector machine (SVM)  is a supervised machine learning classifier. The support vectors lie on the dotted hyperplanes parallel to the separating hyperplane. The margin, the minimum gap between the supporting hyperplane and the separating hyperplane, is chosen to be maximum. The pseudo code is a common, abstract description of implemented SMO computer programs. Because SMO is an algorithm for solving the SVM optimization problem, it corresponds to the model constructor and is an abstract version of the quasi-testable core.\par
Main tasks:
\begin{itemize}
  \item Obtain pseudo oracles.
  \begin{itemize}
    \item MR for Pseudo Oracles: Various combinations of the dataset is obtained by reordering the dataset.
    \item MR for Dataset Generation: Dataset is increased to increase the population of the input dataset.
  \end{itemize}
  \item Generate data points that achieve the required dataset coverage: In order that the result is predictable, the population distribution of the initial dataset is simple enough to contain linearly separable data points. Then a series of tests with pseudo oracles that are obtained based on appropriate metamorphic properties is conducted. Then dataset is extended by adding new data points to calculate a new hyperplane.
\end{itemize}
A similar metamorphic testing approach can be applied to K-nearest neighbors and naive Bayes classifiers. Since testing the whole program at once is not always possible choosing a right SUT from a non-testable program has a large impact on testing activities.

\cite{Segura2016}
Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations. The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions. Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other. The composition is sensitive to the order of metamorphic relations and generalizable to any number of them. Determining whether two metamorphic relations are composable is a manual task. Chen et al. \cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations. In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames. The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

>>>>

\section{Metamorphic Testing Machine Learning Programs}

In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. Non-testable programs can be tested in the following ways:
\begin{itemize}
  \item Creating multiple implementations of the same program and testing them on the same inputs and comparing the results. If the outputs are not the same then either of the implementations may contain an error. This approach is called pseudo-oracle.
  \item In the absence of multiple oracles, metamorphic testing can be used. In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs. If similar outputs are not observed then there must be a defect.
\end{itemize}

Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations to transform inputs. Murphy, Kaiser, Hu, and, Wu (2008) created a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning software. These set of properties can be used to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications\cite{Murphy2008}. They investigated two supervised algorithms MartiRank and SVM-Light and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms. Similar work has also been done by Xie et al. (2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model. The algorithm then performs similar operations from the model on the test data to produce a ranking list. 
SVM-Light is an open-source implementation of SVM that also has a ranking mode.
PAYL is an unsupervised machine learning application which is used to perform intrusion detection. It's dataset simply consist of TCP/IP network payloads(a stream of bytes) without any label or classification.

Based on the analysis of the MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model. Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before. The metamorphic properties identified were: addition and multiplication.  Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs, thus, MartiRank also has permutative metamorphic property. Multiplying the data by a negative constant value will create a new sorting order which can easily be predicted. The only change to the model will be the sorting direction i.e. the algorithm will change the sorting direction but keep the sorting order intact. Therefore, MartiRank also displays an invertive metamorphic property where the new output can be predicted by taking the opposite order of the original output. MartiRank also includes inclusive and exclusive metamorphic properties. Knowing the model can help predict the position of any new elements. Similar properties are also exhibited by SVM-Light and PAYL. If the training and testing data set were transformed using an additive, multiplicative, and/or invertive relationship, then the corresponding model (hyper-plane) would be affected by being shifted, expanded, or inverted in the N dimensions. The resulting ranking of the new model applied to the new data set would be the same as the original model applied to the original dataset because each example (or point in N dimensions) would similarly be moved, and the relative distances would stay the same. SVM considers each example in the testing data independently and ranks according to the distance from the hyperplane, therefore, it has the inclusive and exclusive property. Similarly, PAYL also considers the existence (or absence) of payloads of certain lengths, and thus certainly has inclusive metamorphic properties. From more study of these applications, the authors conclude that even though this not an exhaustive list of metamorphic relations, these metamorphic properties serve as a foundation for determining the relationships and transformations that can be used for conducting metamorphic testing.

Xie et al. (2009) were also building on the previous work and exploring the metamorphic relations based on the expected behavior of given machine learning problems. They present a case study on Weka, a popular machine learning framework, which is also the foundation for computational science tools such as BioWeka in bioinformatics. The authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms. NBC and k-NN both calculate the mean and standard deviation of the input data. The authors identified the metamorphic relations for the two algorithms (k-NN and NBC).
Permuting the order of input data does not affect the mean or standard deviation.
Multiplying the data with -1 does not affect the standard deviation since the deviation from the mean will still be the same.
Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.

They created a set of random input data and used the above metamorphic relationships to generate another set of inputs. Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithms. Using this set of MR the authors were able to uncover a defect in NBC implementation. In the case of the k-NN algorithm, none of the necessary MRs was violated
From the study of these algorithms, the authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
\begin{enumerate}
  \item Consistency with affine transformation.
  \item Permutation of class labels.
  \item Permutation of attributes.
  \item Addition of uninformative/informative attributes.
  \item Consistency with re-prediction.
  \item Addition of training samples.
  \item Addition of classes by duplicating/re-labeling samples.
  \item Removal of classes/samples.
\end{enumerate}
Next, the authors introduce the notion of validation and verification. Validation refers to choosing the most appropriate algorithm to solve a problem. Verification refers to whether the implemented algorithm is correct or not. Current, software testing methods have not addressed the problem of validation and only focus on verification.

Chen et al. \cite{Chen2016} also presented a specification-based tool called METRIC for the identification of metamorphic relations. In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames. The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

Sometimes a single metamorphic property is not enough to uncover defects and we have to use multiple properties. These multiple properties can be applied in any combination. Segura did an research on how to combining these properties
\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively. In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation. \par
New metamorphic relations can be constructed by combining several existing relations. This is called Composition of Metamorphic Relations (CMR)\cite{Segura2016}. The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions. Two metamorphic relations are considered "compositable" if the follow-up test cases of one of the relations can always be used as a source test case of the other. The composition is sensitive to the order of metamorphic relations and generalizable to any number of them. Determining whether two metamorphic relations are composable is a manual task.

### 2019-08-25 chapters/litReview/finalLit.tex
Updates from Overleaf

\section{Software testing}
Testing is one of the most important activity in software development life cycle. Bertolino (2007) define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions". Testing is widely used in industry for quality assurance purposes. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service, etc.\cite{Bertolino2007} A study by Beizer (2006) has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement.\cite{Beizer1990} 
Weyuker (1982) categorizes the testing research activities into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}

However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs. These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle. \cite{Chen2002} \cite(Elbaum2014)
Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}\cite{Weyuker}

 One of the first problems that testers run into is that they don't have access to acceptable output to test the program output against. This problem is often referred to as the Oracle problem. Weyuker provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts. As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.\cite{Weyuker}

 A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time.\cite(Elbaum2014)

 Many techniques have since been developed to test these set of non-testable programs. One way of elevating the oracle-problem is through the use of pseudo oracle. It is also referred to as dual-coding and is used in highly critical software.\cite{Weyuker}\cite{Murphy2009}. Pseudo-oracles are multiple implementation of same specification of the original program under test.
 However, dual coding comes with it's own set of problems. As the authors [this and this ] pointed out that pseudo-oracle requires at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
 In light of shortcomings of the testing process the authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.\cite(Weyuker)

But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation.  
A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors. \cite{Weyuker}

Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer. In such cases, we make use of partial oracles. It is relatively easier to test the systems on simpler inputs for which the output is known. There is rarely a single correct answer in these types of computations. Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution.

>>>>

\section{Software testing}
Testing is one of the most important activity in software development life cycle. Bertolino \cite{Bertolino2007} define software testing as, ``observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions.'' Testing is widely used in industry for various quality assurance purposes. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.
Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}

However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs. These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, the two very obvious fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle \cite{Chen2002,Elbaum2014}.
Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in \cite{Weyuker}:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}

 One of the first problems that testers run into while testing these uncertain programs is that they don't have access to acceptable output to test the program's predictions against. This problem is often referred to as the Oracle problem. Weyuker \cite{Weyuker} provides founding definition of an oracle as "a system that determines the correctness of the solution by comparing the system's output to the one that it predicts". She also defines non-testable programs as the programs for which such oracles do not exist. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.

 A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.

 Many techniques have since been developed to test these set of non-testable programs. One way of elevating the oracle-problem is through the use of pseudo oracle. It is also referred to as dual-coding and is used in highly critical software \cite{Weyuker,Murphy2009}. Pseudo-oracles are multiple implementation of same specification of the original program under test.
 However, dual coding comes with it's own set of problems. As the authors Weyuker \cite{Weyuker} and Murphy, Shen, and, Kaiser \cite{Murphy2009} pointed out some limitations that pseudo-oracles require at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
 In light of these shortcomings of the testing process Weyuker \cite{Weyuker} finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

Due to a great deal of overhead involved, pseudo-oracles may not be practical for every situation.  
A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors. \cite{Weyuker}
